%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-10pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\newcommand{\resumeItemWithoutTitle}[1]{\item\small{{\vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Jared Baur}} & Email: \href{mailto:jaredbaur@fastmail.com}{jaredbaur@fastmail.com}\\
\href{https://github.com/jmbaur}{GitHub: https://github.com/jmbaur}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Occidental College}{Los Angeles, CA}
{Bachelors - Physics \& Mathematics}{August 2015 - May 2019}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Sports:} Played 4 years
			on the Occidental NCAA baseball team}}}
{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Extra curricular:}
			Mentored for 1 year with CollegeSpring for low-income students in the community
			in preparation for college applications and SAT tests.}}}
\resumeSubheading
{DevMountain}{Tempe, AZ}
{Software Development Bootcamp Honors Graduate}{January 2020 - May 2020}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{~~~~~~Rust, Go, C, Zig, Python, Nix, SQL, Bash}
\resumeSubItem{Tools}{~~~~~~~~~~~~~~Nix, Docker/Podman/Nspawn, Git, PostgreSQL, MySQL, SQLite, SSH}
\resumeSubItem{Platforms}{~~~~~~~Linux, NixOS, Web, AWS}
% \resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Anduril Industries}{Costa Mesa, CA}
{Software Engineer (full-time)}{March 2023 - April 2025}
\resumeItemListStart
\resumeItem{NixOS on Embedded}{Provided superior platform support for NixOS on
embedded platforms such as NVIDIA Jetson, NXP IMX8, and Xilinx Zynqmp/Versal.
This involved bootloader (U-Boot, EDK2) and Linux kernel bringup on custom
carrier boards and peripherals used by various products.}
\resumeItem{Security}{Implemented custom program for writing OTP fuses on
Xilinx Zynqmp/Versal boards. This involved writing a baremetal program that
would accept a payload of data to write to the fuses, validating the data for
the current board being ran on, then performing the fusing. This was crucial
for implementing verified boot on Xilinx platforms.}
\resumeItem{Testing}{Maintained and improved upon a custom hardware testing
platform for 50+ individual devices. This involved testing various aspects of a
device's lifecycle, such as firmware updates, NixOS installations, and tests
that perform various platform and hardware specific functions.}
\resumeItem{Manufacturing}{Created and maintained NixOS modules for the purpose
of manufacturing new NixOS devices. Aided in rolling this out to various teams
and products on the manufacturing floor. This included bootstrapping devices
with platform firmware, fusing devices for the purpose of verified boot, and
performing NixOS installations over the network.}
\resumeItemListEnd

\resumeSubheading{Adobe, Inc.}{Remote}
{Software Engineer (full-time)}{May 2022 - March 2023}
\resumeItemListStart
\resumeItem{Site Reliability}{Implemented new features for and maintained a
service aimed at performing automatic remediation of issues encountered for
analytics services within the company. This service was capable of monitoring
hundreds of other services and made the lives of on-call technicians easier by
performing many tasks for them. New features implemented included adding
internal team monitoring, adding integration for new analytics services, and
creating common abstractions around existing services.}
\resumeItemListEnd

\resumeSubheading{Prenda, Inc.}{Remote}
{Software Engineer (full-time)}{August 2020 - April 2022}
\resumeItemListStart
\resumeItem{Authn/Authz}{Implemented an authorization server that enabled other
services to create a root of trust for their consumers. The server used
JWT/JWKs as an interface to other services (implementing RFCs 7517 \& 7519),
which allowed services to ensure authentication and gather authorization
details of a specific principal.}
\resumeItem{Infrastructure}{Utilized the AWS CDK tool to create a library
developer teams could consume to create their desired infrastructure. This
included CI/CD pipelines, integration of custom Cloudformation resources to
manipulate infrastructure in Cloudflare, as well as better defaults for
resources that do networking to enable a dual-stack setup. The usage of the
library led to an increase in holistic quality of infrastructure and enabled
product teams to meet deadlines with an increase in iteration time and
developer productivity.}
\resumeItemListEnd

\resumeSubheading
{CSAA}{Glendale, AZ}
{IT Technician (full-time)}{September 2019 - January 2020}
\resumeItemListStart
\resumeItem{Automation}{Wrote shell scripts to automate employee provisioning
steps, taking a step that took hours manually down to minutes}
\resumeItem{Virtualization}{Worked with virtualization solutions to aid in
software development testing environments.}
\resumeItemListEnd

\resumeSubheading
{Abbott Laboratories}{Sylmar, CA}
{Data Analyst (full-time intern)}{June 2018 - December 2018}
\resumeItemListStart
\resumeItem{Public Image Project}{Led a new project to raise awareness of
company public image through data analysis and automation. Python was utilized
to create a tool that could scrape various social media sites for posts about
the company, perform sentiment analysis of said posts, and then automate the
pipeline so that relevant teams were always kept up to date on the latest
posts. This led to increased focus and prioritization on happy and unhappy
customers alike, allowing for better planning of customer interaction
(conventions, meetings, etc).}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \vspace{-5pt}
% \section{Projects}
% \resumeSubHeadingListStart
% \resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
% \vspace{2pt}
% \resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
% 	faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
% \vspace{2pt}
% \resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
% \vspace{2pt}
% \resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
% \vspace{2pt}
% \resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
% \resumeSubHeadingListEnd

\end{document}

